<!-- Specify the report's official name, goal & description. -->
# Diagnosis of Coupon Pit Depth

**Report Description**: This report is more for the diagnosis of the MCMC.  The `CouponDepth` report is intended for general audiences.

```{r, echo=FALSE} 
  #Set the chunks' working directory to the repository's base directory; this assumes the report is nested inside of two directories.
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -espeically one that uses file paths.
```
<!-- Point knitr to the underlying code file so it knows where to look for the chunks. -->
```{r SetOtherOptions , echo=FALSE, message=F}
  opts_chunk$set(
    comment="" 
    , fig.width = 8
    , fig.height = 10
    , fig.path = 'FigureDiagnosisRmd/' 
  )
  options(width=150)
                 
  # require(xtable)
  # require(scales)
  pathSourceCode <- "./Code/EstimateMlmMcmc/EstimateMlmMcmc.R"
  read_chunk(pathSourceCode) 
```

<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=FALSE, message=FALSE}
```

<!-- Load any Global Functions declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=FALSE, message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=FALSE, message=FALSE}
```

<!-- Load the dataset.   -->
```{r LoadData, echo=F, results='hide', message=F}
```

<!-- Tweak the dataset.   -->
```{r TweakData, echo=F, results='hide', message=F}
```

<!-- Prepare the parameters to be sent to the MCMC.   -->
```{r PrepareMcmc, echo=FALSE, fig.width=10}
```

## 1. Parameters
**chainCount**: `r chainCount`

**iterationCount**: `r iterationCount` (The number used for estimate -ie, it doesn't include burn-in.)

**burninCount**: `r burninCount`

```{r, echo=FALSE}
#   str(dataList)
```


## 2. MCMCglmm

```{r RunMCMCglmm, echo=FALSE}
```

### For and explanation of the graphs, see http://xavier-fim.net/packages/ggmcmc/
```{r GraphJagsSelect, echo=FALSE, fig.height=8}
```

```{r GraphJagsAll, echo=FALSE, fig.height=8}
```

## 3. Display Syntax of Models

```{r DisplayModels, echo=FALSE}
```

## --Session Info--
```{r settings, echo=FALSE}
cat("Report created by", Sys.info()["user"], "at", strftime(Sys.time(), "%F, %T %z"))
sessionInfo()
```