Coupon Depth
=================================================
This report summarizes the pit depths in the coupons exposed to different treatment media.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of only one directory. -->
<!-- Don't combine this call with any other chunk -especially one that uses file paths. -->
```{r, echo=TRUE, message=F} 
  opts_knit$set(root.dir='../')  
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=TRUE}
require(knitr)
opts_chunk$set(
    results='show', 
    comment = NA, 
    tidy = FALSE,
    dpi = 100,
    fig.width = 7, 
    fig.height = 4, 
    fig.path = 'figure_raw/'
)
#     dpi = 400
#     out.width = "600px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- TRUE
options(width=120) #Widen the default text output by 50%  more characters..
read_chunk("./Analysis/CouponDepth.R") 
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r LoadData, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r TweakData, echo=echoChunks, results='show', message=FALSE}
```

## 1. Histogram Overlay
The **first graph** represents the probe heights, as a distance from the coupon's surface.  Each curve represents a histogram.  The *y* value is the depth of the probe, while the *x* indicates how much of the coupon has pits of that depth.  Th diamonds indicate a *treatement's* mean depth. The ticks on the right side indicate a *coupon's* mean depth.

The **second graph** is almost identical to the first, but with two differences.  First, each treatment has its own facet.  Second, the standard errors are shown around each treatment mean; the means and errors were estimated with a multilevel model, shown below.  

The **third graph** is identical, yet loosens the *y*-axis range so that the full depth of the pits are visible.  Consider if a coupon's maximum pit depth is a variable worth including in a formal analysis.

The five outlier coupons are *excluded* from these two graphs (*ie*, the four processed by ConocoPhillips's machine, and one suspicious control coupon).  

The diamonds/means for `AcetateOnly` and `MediaControls` are on top of each other.

```{r HistogramOverlay, echo=FALSE, results='asis', message=TRUE, fig.height = 10}
```

## 2. Coupon Summary Boxplot
The first boxplot shows all points; the four coupons processed on ConocoPhillips machine are marked with a regular triangle.  Another suspicious coupon (in `MediaControls`) is marked with an upside-down triangle.  The second boxplot excludes those five coupons; notice the scale of the *y*-axis has changed.

```{r CouponSummaryBoxplot, echo=echoChunks, results='asis', message=TRUE}
```

## 3. Estimates from MLM (multilevel model) to Test Hypotheses
The five outlier coupons are *excluded* from these two graphs (*ie*, the four processed by ConocoPhillips's machine, and one suspicious control coupon).

Model, with treatment coefficients expressed as offsets.  For more information about the MCMC, see `r pathMcmcCode` and it's html output.

```{r MlmEstimates, echo=FALSE,  message=TRUE}
```

Model, with treatment coefficients expressed as offsets.

```{r MlmCoefficients, echo=FALSE, results='asis', message=TRUE}
```

## 4. Other Models (NOT to be used to Test Hypotheses)
These models are mostly to check the validity & bounds for the MLM estimates in the previous section.  Notice the point estimates for each treatment are very similar (to each other and to the previous MLM).  But the standard errors and *p*-values are very different for the 'no pooling' model, and would lead to different conclusions.  The results for the MLM and pooled

```{r OtherModels, echo=TRUE, message=TRUE}
```

## Session Information
For the sake of documentation and reproducibility, the current report was build on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report created by", Sys.info()["user"], "at", strftime(Sys.time(), "%F, %T %z"))
sessionInfo()
```
